Diagnostics

### 2020-08-05 output_scripts/Diagnostics.Rmd
add some words

data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"

@@

# Correction to Pair level rates

A previous bug with C-MMHP was not correctly accounting for the degree 
corrected `lambda0` and corresponding
`lambda1` between each pair when interpolating the latent states and then 
identifying the residual matrices. This gives more reasonable results for
overall model fit in terms of the total Pearson residuals summed across all 
observation windows.

@@

@@

@@

>>>>

#data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior/"

@@

<!-- # Correction to Pair level rates -->

<!-- A previous bug with C-MMHP was not correctly accounting for the degree  -->
<!-- corrected `lambda0` and corresponding -->
<!-- `lambda1` between each pair when interpolating the latent states and then  -->
<!-- identifying the residual matrices. This gives more reasonable results for -->
<!-- overall model fit in terms of the total Pearson residuals summed across all  -->
<!-- observation windows. -->

# Pearson Residuals

We first compute the Pearson residuals for each of the proposed models for
each of the 10 cohorts. Here I-MMHP is the unconstrained model which
does not learn a latent ranking.

@@

We can then plot the estimated latent ranks from C-MMHP to the 
I&SI ranks. They are highly correlated but not identical (I&SI only using counts 
rather than the times of interactions).

@@

Similarly we can plot the out/in degree parameters of the C-MMHP model
against both the I&SI ranking and also the latent ranking from the
model. This indicates that these degree parameters capture a different structure
to just the dominance of the animals.

@@

As a further model checking, for each cohort we take the
pair with the most interactions and the window which contains the
most interactions for this pair and plot the estimated intensity and
the corresponding QQ plot.
